\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-30 paper/subdocuments/data.Rnw
fixed 1 latex error

Most studies on inequality focus on income inequality solely. However, recent activities emphasize the need of a broader conceptualization. A recent publication from the \citet{oecd_oecd_2013} condense these ideas into the ICW framework (income, consumption and wealth), which is meant to be an internationally agreed framework on micro-level statistics.\footnote{Harmonization with other international standards was an important objective that guided the work of the expert group in developing the ICW Framework presented in this publication. Considered main standards were the System of National Accounts \citep{sna_system_2008}, the Canberra Group Handbook on Household Income Statistics \citep{united_nations_canberra_2011}, the final report of the 17th International Conference of Labour Statisticians \citep{international_labour_organisation_ilo_final_2004}} and the UNECE/CES recommendations for the 2010 Censuses of Population and Housing \citep{unece_conference_2006}}. According to the framework it is best to look at income, consumption and wealth as three separate but interrelated dimensions of people's economic well-being. To gain policy relevant insight, it is recommended to look at the distribution of all three distributions simultaneously. Some households with low income, for example, may report adequate levels of consumption expenditure or wealth holdings, or vice-versa. But it is also stated \citep[18]{oecd_oecd_2013}:"[...] integrated analysis at the household level has significant data requirements that go beyond the measurement efforts currently undertaken in most countries."\footnote{The Luxembourg Wealth Study Database is currently facing this shortcomings by collecting and providing a database following this broader concept of economic well-being. \url{http://www.lisdatacenter.org/our-data/lws-database/}} \\

>>>>

Most studies on inequality focus on income inequality solely. However, recent activities emphasize the need of a broader conceptualization. A recent publication from the \citet{oecd_oecd_2013} condense these ideas into the ICW framework (income, consumption and wealth), which is meant to be an internationally agreed framework on micro-level statistics.\footnote{Harmonization with other international standards was an important objective that guided the work of the expert group in developing the ICW Framework presented in this publication. Considered main standards were the System of National Accounts \citep{sna_system_2008}, the Canberra Group Handbook on Household Income Statistics \citep{united_nations_canberra_2011}, the final report of the 17th International Conference of Labour Statisticians \citep{international_labour_organisation_ilo_final_2004} and the UNECE/CES recommendations for the 2010 Censuses of Population and Housing \citep{unece_conference_2006}}. According to the framework it is best to look at income, consumption and wealth as three separate but interrelated dimensions of people's economic well-being. To gain policy relevant insight, it is recommended to look at the distribution of all three distributions simultaneously. Some households with low income, for example, may report adequate levels of consumption expenditure or wealth holdings, or vice-versa. But it is also stated \citep[18]{oecd_oecd_2013}:"[...] integrated analysis at the household level has significant data requirements that go beyond the measurement efforts currently undertaken in most countries."\footnote{The Luxembourg Wealth Study Database is currently facing this shortcomings by collecting and providing a database following this broader concept of economic well-being. \url{http://www.lisdatacenter.org/our-data/lws-database/}} \\
